### 2023-09-18 manuscript.tex
Accepted! [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/4b17b5aadc8f896a77b0e0ad3ef169ff6e149830.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/4b17b5aadc8f896a77b0e0ad3ef169ff6e149830/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/6219737950

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{archived here}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...c89de3aab786e55c724102ed14dbb33fb23561e5\#files_bucket}{is further updated} since re-submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/c89de3aab786e55c724102ed14dbb33fb23561e5/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/c89de3aab786e55c724102ed14dbb33fb23561e5}{habi/EAWAG-manuscript@c89de3a}
on September 14, 2023.

@@

\leavevmode\vadjust pre{\hypertarget{ref-3rxGCEvJ}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Available: \url{https://osf.io/ecmz4}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{OpenSCAD. {[}cited 14 Sep 2023{]}. Available: \url{https://openscad.org}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wIfTDBqd}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+3.gc52eec3.dirty documentation. {[}cited 14 Sep 2023{]}. Available: \url{https://image.dask.org/en/latest/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-rn6XbmFW}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 14 Sep 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}

>>>>

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{archived here}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...4b17b5aadc8f896a77b0e0ad3ef169ff6e149830\#files_bucket}{is further updated} since re-submission.}
\emph{The manuscript ``has been judged scientifically suitable for publication and will be formally accepted for publication once it meets all outstanding technical requirements'' by PLOS ONE.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/4b17b5aadc8f896a77b0e0ad3ef169ff6e149830/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/4b17b5aadc8f896a77b0e0ad3ef169ff6e149830}{habi/EAWAG-manuscript@4b17b5a}
on September 18, 2023.

@@

\leavevmode\vadjust pre{\hypertarget{ref-3rxGCEvJ}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Summers AP. CT Scans - \#ScanAllFish. 2015 {[}cited 18 Sep 2023{]}. Available: \url{https://osf.io/ecmz4/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{OpenSCAD. {[}cited 18 Sep 2023{]}. Available: \url{https://openscad.org}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wIfTDBqd}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+3.gc52eec3.dirty documentation. {[}cited 18 Sep 2023{]}. Available: \url{https://image.dask.org/en/latest/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-rn6XbmFW}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 18 Sep 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
